A Comprehensive Dataset of U.S. Laws

### 2023-08-10 draft/v1.tex
Updates from Overleaf

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\linenumbers

@@

The reference counts for total laws that we rely on comes from Appendix F reported in Galloway and Wise's History of the House of Representatives\nocite{gallowaywise}, and also previously used for validation and analysis by Ansolabhere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016} Our definition of law is slightly more capacious than Galloway and Wise's, in the sense that we also consider "Joint Resolutions" laws, and the authors admit their own counts combine acts and resolutions (the latter of which are not, in our view, best understood as laws) from the 77th Congress and after. Figure \ref{fig:totals} compares the counts for this key subset of our data. Note that the total deviation in counts is 3. An undergraduate research assistant further investigated the difference in counts of laws in Congress A and B. In both cases, the number of laws that the research assistant counted in that Congress was the same as the number we provided.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{0.4\textwidth}
    \centering
    \includegraphics[width=\linewidth]{draft/figures/.jpg}
    \caption{Caption for Figure 1}
    \label{fig:subfig1}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.4\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure2.jpg}
    \caption{Caption for Figure 2}
    \label{fig:subfig2}
  \end{subfigure}
  \caption{Comparing the count of laws between Galloway \& Wise's Appendix F to the equivalent subset of this paper's replication data.}
  \label{fig:main}
\end{figure}

A second

>>>>

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\usepackage{subcaption}
\linenumbers

@@

The reference counts for total laws that we rely on comes from Appendix F reported in Galloway and Wise's History of the House of Representatives\nocite{gallowaywise}, and also previously used for validation and analysis by Ansolabhere, Palmer, and Schneer.\cite{ansolabehere_palmer_schneer_2016} Our definition of law is slightly more capacious than Galloway and Wise's, in the sense that we also consider "Joint Resolutions" laws, and the authors admit their own counts combine acts and resolutions (the latter of which are not, in our view, best understood as laws) from the 77th Congress and after. Figure \ref{fig:totals} compares the counts for this key subset of our data. Note that in total Galloway and Wise count 23,155 laws while we would peg the figure at 23,152, a total difference of 3 laws ($\approx 0.13\%$ of the total). The true discrepancy is somewhat greater, as the Figure reveals, because in some years our counts are higher than Galloway \& Wise's, however in all but six Congresses our counts are identical. Summing up the absolute value of the difference in counts in these six Congresses, we arrive at a total difference of 11. An undergraduate research assistant further investigated the difference in counts of laws in Congress A and B. In both cases, the number of laws that the research assistant counted in that Congress was the same as the number we provided.

\begin{figure}
    \centering
    \includegraphics{draft/figures/counts_of_laws  
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}
A second
